### 2021-02-16 Chapter-1/Chapter-1.tex
update

\begin{itemize}
    \item It is hard to identify side-channel vulnerabilities in real-world software. In general, many side-channel vulnerabilities are low-level problems. Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs. Recent work can identify side-channel leakages. But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis. 
    \item Side-channel vulnerabilities are ubiquitous. While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit. Moreover, some vulnerable implementations perform better. Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.  
\end{itemize}

\section{Contribution}
To address the above problems, we make the following contributions in this dissertations:

\begin{itemize}
    \item We propose a novel method that can quantify fine-grained leaked
    information from side-channel vulnerabilities that result from actual attack
    scenarios in a single trace attack. Our approach differs from previous ones in that we
    model real attack scenarios for one execution. 
    We model the information quantification problem as a counting problem 
    and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it
    to several pieces of real software. \tool{} successfully identifies
    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
    Our results are useful in practice.
    The leakage estimates and the corresponding trigger inputs can 
    help developers to triage and fix the vulnerabilities.
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}

>>>>

\begin{enumerate}
    \item It is hard to identify side-channel vulnerabilities in real-world software. In general, many side-channel vulnerabilities are low-level problems. Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs. Recent work can identify side-channel leakages. But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis. 
    \item Side-channel vulnerabilities are ubiquitous. While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit. Moreover, some vulnerable implementations perform better. Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.  
\end{enumerate}

\section{Contribution}
To address Problem 1, we make the following contributions on detecting side-channel leakages:

\begin{itemize}
    \item We designs a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data access. The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
    \item We implement the above method in a tool called ~\detect{}. The evaluation results shows that ~\detect{}  is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library. Additional, we do not need to apply domain knowledge to only part of the original program, which simplify the analysis. 
\end{itemize}

To address Problem 2, we make the following contributions on quantifying side-channel leakages:

\begin{itemize}
    \item We propose a method that can quantify fine-grained leaked
    information from side-channel vulnerabilities that result from actual attack
    scenarios in a single trace attack. Our approach differs from previous ones in that we
    model real attack scenarios for one execution. 
    We model the information quantification problem as a counting problem 
    and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it
    to several pieces of real software. \tool{} successfully identifies
    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
    Our results are useful in practice.
    The leakage estimates and the corresponding trigger inputs can 
    help developers to triage and fix the vulnerabilities.
    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically. Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages. The method can combine multiple leakage sites to retrieve more information as well.
    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity. We propose a method that can estimate the lower bound of information leakages. The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK. The results show that our tool can detect and quantify the side-channel leakages effectively. Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
\end{itemize}
